---
title: "01-assignment_lin"
author: "Chau-Fang Lin"
date: "8/28/2019"
output: html_document
---

# Assignment 1


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Load libraries needed for assignment

library(tidyverse)
library(Metrics)
library(plotly)
```

## Question 1

1. Print Hello, World

```{r hello world}

##Print Hello, World

"Hello, World"

```

## Question 2.1

```{r college data income}

# Load college. Rdata

load ("college.Rdata")

# Calculate the average earnings for the most selective schools

sc%>%filter(adm_rate<.1)%>%summarize(mean_earnings=mean(md_earn_wne_p6, na.rm = TRUE))

# Calculate the average earning for the least selective school

sc%>%filter(adm_rate>.3)%>%summarize(mean_earnings=mean(md_earn_wne_p6,na.rm = TRUE))

```

The average earnings of students who attended the most selective selective (admit rate < 10%) colleges (53,500) is greather than the average earnings of studentswho attended the lease selective (admit rate > 30%) colleges (34,747.14).

## Question 2.2

```{r college data SATsize}

# Calculate average number of undergrads for schools with high average SAT scores

sc%>%filter(sat_avg>1400) %>% summarize(mean_ugrads=mean(ugds))

# Calculate average number of undergrads for schools with low average SAT scores

sc%>%filter(sat_avg<1000) %>% summarize(mean_ugrads=mean(ugds))

```
Colleges with students who have high average SAT scores (average SAT > 1400) tend to be larger than colleges with students who have low average SAT scores (average SAT score < 1000).

## Question 2.3

```{r cost x debt plot}

# Plot the relationship between cost and debt.

gg_costdebt <- ggplot(data=sc, aes(x=costt4_a,y=debt_mdn, text=instnm))

gg_costdebt <- gg_costdebt + geom_point(alpha=.5,size=1)

gg_costdebt <- gg_costdebt+xlab("Cost")+ylab("Debt")

gg_costdebt

```

The scatter plot of the cost and debt by institution suggest that there is no relationship between the cost to attend an institution and the amount of debt that a student accrues.

## Question 2.4

```{r control}

# Provide separate plots of cost and debt by control of institution.

gg_costdebt + facet_wrap(~control,nrow=1)

```

